Rheology of Cubic Blue Phases

### 2013-06-09 papers/bprheo/bprheo.tex
Update bprheo paper
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2002 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}[htpb]
\includegraphics[width=0.495\textwidth]{flowcurve_bp1.pdf}\\
\caption{Flow curve $\bar{\Pi}_{xy}(\gd)$: 
\rev{Depending on the configuration in steady shear flow five different regimes 
can be identified: amorphous BP network with yield stress (BPI-1, solid squares), 
steady flow with periodically recurring patterns (BPI-2, open squares), 
breakup of the disclination network into amorphous state (BPI-3, open circles)
and metastable configurations (BPI-3, solid circles), 
cholesteric helix with axis in gradient direction (BPI-4, open triangles) 
and flow-aligned nematic state (BPI-5, solid triangles). 
The error bars represent the minimum and maximum shear stress 
during one cycle in regime BPI-2.}}
\label{bp1-flowcurve}
\end{figure}

>>>>

\begin{figure}[htpb]
\includegraphics[width=0.495\textwidth]{flowcurve_bp1.pdf}\\
\caption{Flow curve $\bar{\Pi}_{xy}(\gd)$: 
\rev{Depending on the configuration in steady shear flow five different regimes 
can be identified: amorphous BP network with yield stress (BPI-1, solid squares), 
steady flow with periodically recurring patterns (BPI-2, open squares), 
breakup of the disclination network into amorphous state (BPI-3, open circles)
and metastable configurations (BPI-3, solid circles), 
cholesteric helix with axis in gradient direction (BPI-4, open triangles) 
and flow-aligned nematic state (BPI-5, solid triangles). 
The error bars represent the minimum and maximum shear stress 
during one cycle in regime BPI-2.
The two dashed lines represent fits to the data in regime BPI-2 with $\bar{\Pi}_{xy}(\gd)\propto \gd^{\;0.84}$ (left) and in regime BPI-4 with $\bar{\Pi}_{xy}(\gd)\propto \gd^{\;1.02}$ (right), respectively.}}
\label{bp1-flowcurve}
\end{figure}
